Software Architectures for Integrating Workflow Engines in Science Gateways

### 2016-05-14 related.tex
again related

>>>>

@article{yuTaxonomy,
	year={2005},
	issn={1570-7873},
	journal={Journal of Grid Computing},
	volume={3},
	number={3-4},
	title={A Taxonomy of Workflow Management Systems for Grid Computing},
	publisher={Springer Netherlands},
	keywords={Grid computing; resource management; scheduling; taxonomy; workflow management},
	author={J. Yu  and R. Buyya},
	pages={171-200},
	language={English}
}

@article{deelmanFGCS,
	TITLE={Workflows and e-Science: An overview of workflow system features and capabilities}, 
	author    = {E. Deelman and
		D. Gannon and
		M. S. Shields and
		I. Taylor},
	JOURNAL={Future Generation Computer Systems}, 
	YEAR={2009},
	VOLUME={25},
	NUMBER={5},
	PAGES={528-540},
}
